A Spatial AR System for Axis-aligned Augmentation of Planar Scenes in Industrial Settings

### 2021-07-14 paper/elsarticle/elsarticle-template.tex
Paper

Keystone correction for planar scenes can be carried out using a 2D homography \cite{Hartley2004}---an invertible transformation that preserves colinearity, hence alternatively termed a `colineation'---and is ultimately the approach we take as well. The intuition for why a transformation that maps lines to lines can serve to model the necessary image warp can be drawn from considering a planar chessboard pattern: looking at an image of a chessboard acquired from an oblique angle, one observes that parallel lines appear to meet in respective vanishing points; looking at an image of the same chessboard acquired frontally with respect to the plane of the chessboard, lines parallel in the chessboard appear parallel in the image (i.e., they are said to meet `at infinity'). To warp the former image (where lines parallel in the scene meet in respective vanishing points) such that the lines of the chessboard appear as in the latter image (where lines parallel in the scene meet at infinity), a transformation that maps lines to lines that would give the desired effect.

>>>>

Keystone correction for planar scenes can be carried out using a 2D homography \cite{Hartley2004}---an invertible transformation that preserves colinearity, hence alternatively termed a `colineation'---and is ultimately the approach we take as well. The intuition for why a transformation that maps lines to lines can serve to model the appropriate image warp can be drawn from considering a planar chessboard pattern: looking at an image of a chessboard acquired from an oblique angle, one observes that lines parallel in the chessboard appear to meet in respective vanishing points; looking at an image of the same chessboard acquired frontally with respect to the plane of the chessboard, lines parallel in the chessboard appear parallel in the image (i.e., they are said to meet `at infinity'). To warp the former image (where lines parallel in the scene meet in respective vanishing points) such that the lines of the chessboard appear as in the latter image (where lines parallel in the scene meet at infinity), a transformation that maps lines to lines that would give the desired effect.
